---
title: "R Notebook"
output: html_notebook
---
# git commit code
```{bash}
git status
git add distribution.Rmd samplesize.Rmd
git commit -m  "spacing issues corrected"
git push -u origin_3 main
```
## Assessment of the normal distribution function for different values of x and y
```{r}

x_vector = c()
y_vector = c()
vector_assess = seq.int(0.001,0.99,0.001)
for (i in seq_along(vector_assess)) {
  x_vector[i] <- vector_assess[i]
  y_vector[i] <- qnorm(vector_assess[i])
  # print(y_vector)
  # print(x_vector)
  
}

# x_vector
# y_vector

plot(x_vector,y_vector)
```

## Assessment of the sigmoid distribution function for different values of x and y
```{r}

x_vector = c()
y_vector = c()
# vector_assess = c(-Inf,-1,0, 1, Inf)
vector_assess = c(-Inf,-100,-50,-10,-9,-8,-7,-6,-5,-4,-3,-2,-1,0,1,2,3,4,5,6,7,8,9,10,50,100,Inf)
for (i in seq_along(vector_assess)) {
  x_vector[i] <- vector_assess[i]
  y_vector[i] <- 1/(1+(1/exp(vector_assess[i])))
  # print(y_vector)
  # print(x_vector)
  
}

# x_vector
# y_vector

plot(x_vector,y_vector,type = "b")
```

# Binomial function created for estimation of probability of success for a given event of interest on providing probability of success and failure along with total number of trials
```{r}
binomial = function(p , q, n, x){
  p = choose(n, x) * p^x * q^(n-x)
  return(p)
}


vector_assess = seq.int(from = 0,to = 100,by = 1)
x_vector = c()
y_vector = c()
for (i in seq_along(vector_assess)) {
  x_vector[i] <- vector_assess[i]
  y_vector[i] <- binomial(p = 0.8,q = 0.2,n = 100,x = vector_assess[i])
   # print(y_vector)
   # print(x_vector)
  
}

# x_vector
# y_vector

plot(x_vector,y_vector,type = "b")
```


# Normal distribution
```{r}

normal_distribution = function(x,mean,sd){
  
  y = (1/sd* sqrt(2* pi))* 1/exp(0.5 * ((x-mean)/sd)^2)
}
# vector_assess = seq.int(from = -1000,to = 1000,by = 1)
vector_assess = seq.int(from = 0,to = 100,by = 1)
x_vector = c()
y_vector = c()

for (i in seq_along(vector_assess)){
  mean = mean(vector_assess,na.rm = TRUE)
  sd = sd(vector_assess,na.rm = TRUE)
  x_vector[i] = vector_assess[i]
  y_vector[i] = normal_distribution(x=vector_assess[i],mean = mean,sd = sd)
  if (i == length(vector_assess)) {
    print(mean)
    print(sd)
  }
}


plot(x_vector,y_vector,type = "b")
```

